Bitmap Indexing for Fast Analysis of Large Astrophysical Datasets

### 2019-06-06 ms/ms.tex
Merge in changes on remote

% For IEEE word count (no figs)
\ieeetrue
\twocolfalse
\placefigtrue
\inclfigtrue
\draftfalse

@@

%---------------------------------------------------------------------------------
% PREAMBLE
\iftwocol
	\documentclass[apjl]{emulateapj}
\else
	\ifieee
		\documentclass[journal]{IEEEtran}
	\else
		\documentclass[preprint]{aastex}
	\fi
\fi

@@

\usepackage{hyperref}

@@

\markboth{Journal of Computing in Science and Engineering,~Vol.~X, No.~X, Month~Year}%
{Bitmap Indexing for Fast Analysis of Large Astrophysical Datasets}

@@

%---------------------------------------------------------------------------------
% CODE
\section*{Code}\label{S:code}
These procedures have been implemented as part of the {\tt yt} python package
\citep{Turk20d11a} in order to facilitate the analysis of large astrophysical
N-body simulations; currently undergoing review for inclusion in a future version of {\tt yt} (3.4 or later), our implementation is available at \url{https://bitbucket.org/langmm/yt-bitmap}. The open source EWAHBoolArray C++ package is used for implementing EWAH bitmaps \citep{Lemire2010,Kaser2016} and exposed to Python using Cython \citep{Behnel2011}.

>>>>

% For IEEE 
\ieeetrue
\twocoltrue
\placefigtrue
\inclfigtrue % false for word count (no figs)
\draftfalse

@@

%---------------------------------------------------------------------------------
% PREAMBLE
\iftwocol
	\ifieee
		\documentclass[journal]{IEEEtran}
	\else
		\documentclass[apjl]{emulateapj}
	\fi
\else
	\ifieee
		\documentclass[peerreview]{IEEEtran}
	\else
		\documentclass[preprint]{aastex}
	\fi
\fi

@@

\usepackage[bookmarks=false]{hyperref}

@@

%\markboth{Journal of Computing in Science and Engineering,~Vol.~X, No.~X, Month~Year}%
%{Bitmap Indexing for Fast Analysis of Large Astrophysical Datasets}

@@

%---------------------------------------------------------------------------------
% CODE
\section*{Code}\label{S:code}
These procedures have been implemented as part of the {\tt yt} python package
\citep{Turk20d11a} in order to facilitate the analysis of large astrophysical
N-body simulations; currently undergoing review for inclusion in a future version of {\tt yt} (3.4 or later), our implementation is available at {https://bitbucket.org/langmm/yt-bitmap}. The open source EWAHBoolArray C++ package is used for implementing EWAH bitmaps \citep{Lemire2010,Kaser2016} and exposed to Python using Cython \citep{Behnel2011}.
